An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-24 paper/paper.tex
Minor changes to the methodology

As we have already discussed, churn is important to consider when designing a realistic P2P backup system. In this test scenario, we measured how well our system handles different levels of churn. To do this, we created a network of 100 peers, in addition to the tracker and the log server. Each peer had a single 1GB file that it tried to back up. This means that, with five replicas per file, there was 600GB of data in the network.

% TODO: When we pick the actual distribution functions, write them in this paragraph.
To create churn, we have peers enter and leave the network at varying time intervals. Running our program signifies when a peer enters the network, while exiting our program signifies leaving the network. Both of these were controlled by a script that we wrote. To determine the duration of time, the script picked a timeout from one of two exponential distributions, depending on whether the peer was entering or leaving the network. This is the strategy used in the experimental results of PeerStore \cite{PeerStore}. By using an exponential distribution, there will be a greater chance of peers going offline for a short amount of time. This is useful, since in a production environment, many nodes will go offline for a short amount of time (i.e. users shutting their machine down at night), but fewer will stay offline for a long period of time or permanently leave the network.

>>>>

As we have already discussed, churn is important to consider when designing a realistic P2P backup system. In this test scenario, we measured how well our system handles different levels of churn. To do this, we created a network of 100 peers, in addition to the tracker and the log server. Each peer had a single 100MB file that it tried to back up. This means that, with five replicas per file, there was 6GB of data in the network.

% TODO: When we pick the actual distribution functions, write them in this paragraph.
To create churn, we have peers enter and leave the network at varying time intervals. Running our program signifies when a peer enters the network, while exiting our program signifies leaving the network. Both of these were controlled by a script that we wrote. To determine the duration of time, the script picked a timeout from one of two distributions, depending on whether the peer was entering or leaving the network. This is the strategy used in the experimental results of PeerStore \cite{PeerStore}.

Our distributions are a combination of three functions over the range $[0,1)$. In order to choose an uptime or downtime, a node chooses a random number in this range, and applies it to the follow function:

$$
f(x)=
\begin{cases}
10xc & \mbox{ if $0 \leq x < 0.2$ } \\
(4(x-0.2)+2)c & \mbox{ if $0.2 \leq x < 0.8$ } \\
(e^{21(x-0.84)}+3.5)c & \mbox{ if $0.8 \leq x < 1$ }
\end{cases}
$$

%By using an exponential distribution, there will be a greater chance of peers going offline for a short amount of time. This is useful, since in a production environment, many nodes will go offline for a short amount of time (i.e. users shutting their machine down at night), but fewer will stay offline for a long period of time or permanently leave the network.
